Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2021-06-16 thirdPaper/draft/typeConeAssociahedra.tex
more details in pf of Cor 4.35

More specifically: fix an additive category~$\cat$, and an additive bifunctor~$\mathbb{E}: \cat^\mathrm{op}\times\cat\to\mathit{Ab}$.

@@

\begin{proof}
First note that any injective object belongs to~$\susp \tc$, by \cref{lem:shifts of extriangles}.
Let us prove that the converse holds.
Let~$\susp T \infl X \overset{f}{\defl} Y\overset{\delta}{\dashrightarrow}$ be an extriangle with~$T\in\tc$.
Since~$\cat(-,\susp T)|_\tc = 0$ and~$f$ is~$\tc$-epic, the morphism~$\cat(-,f)|_\tc$ is an isomorphism in~$\modt$.
By \cref{prop:KRextricat}, there are morphisms~$Y\overset{s}{\to} X$,~$Y\xrightarrow{h}\susp T'$,~$\susp T'\xrightarrow{t} Y$, for some~$T'\in\tc$ satisfying
\[
fs = id_Y + th.
\]
By \cref{lem:first consequences}\,(v), $\susp\tc$ is a rigid subcategory, so that~$t^\ast\delta=0$.
Equivalently, there is a morphism~$\susp T'\xrightarrow{k} X$ such that~$t=fk$.
We thus have~$f(s-kh)=id_Y$, showing that the extriangle splits.
\end{proof}

>>>>

More specifically: fix an additive category~$\cat$, and an additive bifunctor~$\mathbb{E}: \cat^\mathrm{op}\times\cat\to\mathit{Ab}$, where $\mathit{Ab}$ is the category of abelian groups.

@@

\begin{proof}
First note that any injective object belongs to~$\susp \tc$, by \cref{lem:shifts of extriangles}.
Indeed, if~$X$ is injective, then the extriangle
\[
X \overset{h_X}{\infl} \susp T_1^X \overset{\susp f_X}{\defl} \susp T_0^X \overset{(g_X)_\ast\delta_0}{\dashrightarrow}
\]
splits, showing that~$X$ is a summand of~$\susp T_1^X$.
Let us prove that the converse holds.
Let~$\susp T \infl X \overset{f}{\defl} Y\overset{\delta}{\dashrightarrow}$ be an extriangle with~$T\in\tc$.
Since~$\cat(-,\susp T)|_\tc = 0$ and
%~$f$ is~$\tc$-epic,
$\mathbb{E}(-,\susp T)|_\tc =0$ (by \cref{lem:first consequences}),
the morphism~$\cat(-,f)|_\tc$ is an isomorphism in~$\modt$.
By \cref{prop:KRextricat}, there are morphisms~$Y\overset{s}{\to} X$,~$Y\xrightarrow{h}\susp T'$,~$\susp T'\xrightarrow{t} Y$, for some~$T'\in\tc$ satisfying
\[
fs = id_Y + th.
\]
By \cref{lem:first consequences}\,(v), $\susp\tc$ is a rigid subcategory, so that~$t^\ast\delta=0$.
Equivalently, there is a morphism~$\susp T'\xrightarrow{k} X$ such that~$t=fk$.
We thus have~$f(s-kh)=id_Y$, showing that the extriangle splits.
\end{proof}
